---
title: "Proportional Occupancy Report"
author: "Juan P Barraza"
date: "October 11, 2017"
output: html_document
---
##dspB data exp #1    

```{r dspB 1, echo=FALSE, fig.width=4, fig.height=3, results='hide', warning=FALSE, message=FALSE}
library(knitr)
rm(list = ls())

source('/Users/jupabago/testRstudioGithub/PropOcFunctions.R')
fileList<-getFiles("~/Dropbox (Whiteley Lab)/BrownWhiteleyShare/2014_11_26RomanTIFFs/Experiment #1/dspB abscess/dspB abscess #1.1")  
NormRawPipeline(thresholdImage(fileList$c1,"red", 512),thresholdImage(fileList$c2,"green", 512),xysize=512, zsize=13,xydimSearch=13,zdimSearch=4,sampleSize=1000,xyRealDim=1.24,zRealDim=4, pipeBinSize = 2)

fileList<-getFiles("~/Dropbox (Whiteley Lab)/BrownWhiteleyShare/2014_11_26RomanTIFFs/Experiment #1/dspB abscess/dspB abscess #1.2")  
NormRawPipeline(thresholdImage(fileList$c1,"red", 512),thresholdImage(fileList$c2,"green", 512),xysize=512, zsize=8,xydimSearch=13,zdimSearch=4,sampleSize=1000,xyRealDim=1.24,zRealDim=4, pipeBinSize = 2)

fileList<-getFiles("~/Dropbox (Whiteley Lab)/BrownWhiteleyShare/2014_11_26RomanTIFFs/Experiment #1/dspB abscess/dspB abscess #1.3")  
NormRawPipeline(thresholdImage(fileList$c1,"red", 512),thresholdImage(fileList$c2,"green", 512),xysize=512, zsize=10,xydimSearch=13,zdimSearch=4,sampleSize=1000,xyRealDim=1.24,zRealDim=4, pipeBinSize = 2)

fileList<-getFiles("~/Dropbox (Whiteley Lab)/BrownWhiteleyShare/2014_11_26RomanTIFFs/Experiment #1/dspB abscess/dspB abscess #2.1")  
NormRawPipeline(thresholdImage(fileList$c1,"red", 512),thresholdImage(fileList$c2,"green", 512),xysize=512, zsize=13,xydimSearch=13,zdimSearch=4,sampleSize=1000,xyRealDim=1.24,zRealDim=4, pipeBinSize = 2)

fileList<-getFiles("~/Dropbox (Whiteley Lab)/BrownWhiteleyShare/2014_11_26RomanTIFFs/Experiment #1/dspB abscess/dspB abscess #2.2")
NormRawPipeline(thresholdImage(fileList$c1,"red", 512),thresholdImage(fileList$c2,"green", 512),xysize=512, zsize=9,xydimSearch=13,zdimSearch=4,sampleSize=1000,xyRealDim=1.24,zRealDim=4, pipeBinSize = 2)

#z-stack is not enough
#fileList<-getFiles("~/Dropbox (Whiteley Lab)/BrownWhiteleyShare/2014_11_26RomanTIFFs/Experiment #1/dspB abscess/dspB abscess #2.3")  
#NormRawPipeline(thresholdImage(fileList$c1,"red", 512),thresholdImage(fileList$c2,"green", 512),xysize=512, zsize=7,xydimSearch=13,zdimSearch=4,sampleSize=1000,xyRealDim=1.24,zRealDim=4, pipeBinSize = 2)

fileList<-getFiles("~/Dropbox (Whiteley Lab)/BrownWhiteleyShare/2014_11_26RomanTIFFs/Experiment #1/dspB abscess/dspB abscess #2.4")  
NormRawPipeline(thresholdImage(fileList$c1,"red", 512),thresholdImage(fileList$c2,"green", 512),xysize=512, zsize=10,xydimSearch=13,zdimSearch=4,sampleSize=1000,xyRealDim=1.24,zRealDim=4, pipeBinSize = 2)

```

##dspB data exp #2    

```{r dspB 2, echo=FALSE, fig.width=4, fig.height=3, results='hide', warning=FALSE, message=FALSE}
library(knitr)
rm(list = ls())
source('/Users/jupabago/testRstudioGithub/PropOcFunctions.R')
fileList<-getFiles("~/Dropbox (Whiteley Lab)/BrownWhiteleyShare/2014_11_26RomanTIFFs/Experiment #2/dspB abscess/dspB abscess #1.1")  
NormRawPipeline(thresholdImage(fileList$c1,"red", 512),thresholdImage(fileList$c2,"green", 512),xysize=512, zsize=12,xydimSearch=13,zdimSearch=4,sampleSize=1000,xyRealDim=1.24,zRealDim=4, pipeBinSize = 2)
fileList<-getFiles("~/Dropbox (Whiteley Lab)/BrownWhiteleyShare/2014_11_26RomanTIFFs/Experiment #2/dspB abscess/dspB abscess #1.2")  
NormRawPipeline(thresholdImage(fileList$c1,"red", 512),thresholdImage(fileList$c2,"green", 512),xysize=512, zsize=12,xydimSearch=13,zdimSearch=4,sampleSize=1000,xyRealDim=1.24,zRealDim=4, pipeBinSize = 2)
fileList<-getFiles("~/Dropbox (Whiteley Lab)/BrownWhiteleyShare/2014_11_26RomanTIFFs/Experiment #2/dspB abscess/dspB abscess #1.3")  
NormRawPipeline(thresholdImage(fileList$c1,"red", 512),thresholdImage(fileList$c2,"green", 512),xysize=512, zsize=15,xydimSearch=13,zdimSearch=4,sampleSize=1000,xyRealDim=1.24,zRealDim=4, pipeBinSize = 2)
fileList<-getFiles("~/Dropbox (Whiteley Lab)/BrownWhiteleyShare/2014_11_26RomanTIFFs/Experiment #2/dspB abscess/dspB abscess #2.1")  
NormRawPipeline(thresholdImage(fileList$c1,"red", 512),thresholdImage(fileList$c2,"green", 512),xysize=512, zsize=10,xydimSearch=13,zdimSearch=4,sampleSize=1000,xyRealDim=1.24,zRealDim=4, pipeBinSize = 2)
fileList<-getFiles("~/Dropbox (Whiteley Lab)/BrownWhiteleyShare/2014_11_26RomanTIFFs/Experiment #2/dspB abscess/dspB abscess #2.2")  
NormRawPipeline(thresholdImage(fileList$c1,"red", 512),thresholdImage(fileList$c2,"green", 512),xysize=512, zsize=14,xydimSearch=13,zdimSearch=4,sampleSize=1000,xyRealDim=1.24,zRealDim=4, pipeBinSize = 2)
fileList<-getFiles("~/Dropbox (Whiteley Lab)/BrownWhiteleyShare/2014_11_26RomanTIFFs/Experiment #2/dspB abscess/dspB abscess #2.3")  
NormRawPipeline(thresholdImage(fileList$c1,"red", 512),thresholdImage(fileList$c2,"green", 512),xysize=512, zsize=15,xydimSearch=13,zdimSearch=4,sampleSize=1000,xyRealDim=1.24,zRealDim=4, pipeBinSize = 2)
fileList<-getFiles("~/Dropbox (Whiteley Lab)/BrownWhiteleyShare/2014_11_26RomanTIFFs/Experiment #2/dspB abscess/dspB abscess #3.1")  
NormRawPipeline(thresholdImage(fileList$c1,"red", 512),thresholdImage(fileList$c2,"green", 512),xysize=512, zsize=17,xydimSearch=13,zdimSearch=4,sampleSize=1000,xyRealDim=1.24,zRealDim=4, pipeBinSize = 2)
fileList<-getFiles("~/Dropbox (Whiteley Lab)/BrownWhiteleyShare/2014_11_26RomanTIFFs/Experiment #2/dspB abscess/dspB abscess #3.2")  
NormRawPipeline(thresholdImage(fileList$c1,"red", 512),thresholdImage(fileList$c2,"green", 512),xysize=512, zsize=16,xydimSearch=13,zdimSearch=4,sampleSize=1000,xyRealDim=1.24,zRealDim=4, pipeBinSize = 2)
fileList<-getFiles("~/Dropbox (Whiteley Lab)/BrownWhiteleyShare/2014_11_26RomanTIFFs/Experiment #2/dspB abscess/dspB abscess #3.3")  
NormRawPipeline(thresholdImage(fileList$c1,"red", 512),thresholdImage(fileList$c2,"green", 512),xysize=512, zsize=17,xydimSearch=13,zdimSearch=4,sampleSize=1000,xyRealDim=1.24,zRealDim=4, pipeBinSize = 2)
```

##wt data exp #1    

```{r wt 1, echo=FALSE, fig.width=4, fig.height=3, results='hide', warning=FALSE, message=FALSE}
library(knitr)
rm(list = ls())
source('/Users/jupabago/testRstudioGithub/PropOcFunctions.R')
fileList<-getFiles("~/Dropbox (Whiteley Lab)/BrownWhiteleyShare/2014_11_26RomanTIFFs/Experiment #1/wt abscess/wt abscess #1.1")  
NormRawPipeline(thresholdImage(fileList$c1,"red", 512),thresholdImage(fileList$c2,"green", 512),xysize=512, zsize=13,xydimSearch=13,zdimSearch=4,sampleSize=1000,xyRealDim=1.24,zRealDim=4, pipeBinSize = 2)
fileList<-getFiles("~/Dropbox (Whiteley Lab)/BrownWhiteleyShare/2014_11_26RomanTIFFs/Experiment #1/wt abscess/wt abscess #1.2")  
NormRawPipeline(thresholdImage(fileList$c1,"red", 512),thresholdImage(fileList$c2,"green", 512),xysize=512, zsize=18,xydimSearch=13,zdimSearch=4,sampleSize=1000,xyRealDim=1.24,zRealDim=4, pipeBinSize = 2)
fileList<-getFiles("~/Dropbox (Whiteley Lab)/BrownWhiteleyShare/2014_11_26RomanTIFFs/Experiment #1/wt abscess/wt abscess #1.3")  
NormRawPipeline(thresholdImage(fileList$c1,"red", 512),thresholdImage(fileList$c2,"green", 512),xysize=512, zsize=12,xydimSearch=13,zdimSearch=4,sampleSize=1000,xyRealDim=1.24,zRealDim=4, pipeBinSize = 2)
fileList<-getFiles("~/Dropbox (Whiteley Lab)/BrownWhiteleyShare/2014_11_26RomanTIFFs/Experiment #1/wt abscess/wt abscess #2.1")  
NormRawPipeline(thresholdImage(fileList$c1,"red", 512),thresholdImage(fileList$c2,"green", 512),xysize=512, zsize=16,xydimSearch=13,zdimSearch=4,sampleSize=1000,xyRealDim=1.24,zRealDim=4, pipeBinSize = 2)
fileList<-getFiles("~/Dropbox (Whiteley Lab)/BrownWhiteleyShare/2014_11_26RomanTIFFs/Experiment #1/wt abscess/wt abscess #2.2")  
NormRawPipeline(thresholdImage(fileList$c1,"red", 512),thresholdImage(fileList$c2,"green", 512),xysize=512, zsize=8,xydimSearch=13,zdimSearch=4,sampleSize=1000,xyRealDim=1.24,zRealDim=4, pipeBinSize = 2)
fileList<-getFiles("~/Dropbox (Whiteley Lab)/BrownWhiteleyShare/2014_11_26RomanTIFFs/Experiment #1/wt abscess/wt abscess #2.3")  
NormRawPipeline(thresholdImage(fileList$c1,"red", 512),thresholdImage(fileList$c2,"green", 512),xysize=512, zsize=17,xydimSearch=13,zdimSearch=4,sampleSize=1000,xyRealDim=1.24,zRealDim=4, pipeBinSize = 2)
```

##wt data exp #2    

```{r wt 2, echo=FALSE, fig.width=4, fig.height=3, results='hide', warning=FALSE, message=FALSE}
library(knitr)
rm(list = ls())
source('/Users/jupabago/testRstudioGithub/PropOcFunctions.R')
fileList<-getFiles("~/Dropbox (Whiteley Lab)/BrownWhiteleyShare/2014_11_26RomanTIFFs/Experiment #2/wt abscess/wt abscess #1.1")  
NormRawPipeline(thresholdImage(fileList$c1,"red", 512),thresholdImage(fileList$c2,"green", 512),xysize=512, zsize=15,xydimSearch=13,zdimSearch=4,sampleSize=1000,xyRealDim=1.24,zRealDim=4, pipeBinSize = 2)
fileList<-getFiles("~/Dropbox (Whiteley Lab)/BrownWhiteleyShare/2014_11_26RomanTIFFs/Experiment #2/wt abscess/wt abscess #1.2")  
NormRawPipeline(thresholdImage(fileList$c1,"red", 512),thresholdImage(fileList$c2,"green", 512),xysize=512, zsize=15,xydimSearch=13,zdimSearch=4,sampleSize=282,xyRealDim=1.24,zRealDim=4, pipeBinSize = 2)
fileList<-getFiles("~/Dropbox (Whiteley Lab)/BrownWhiteleyShare/2014_11_26RomanTIFFs/Experiment #2/wt abscess/wt abscess #1.3")  
NormRawPipeline(thresholdImage(fileList$c1,"red", 512),thresholdImage(fileList$c2,"green", 512),xysize=512, zsize=15,xydimSearch=13,zdimSearch=4,sampleSize=289,xyRealDim=1.24,zRealDim=4, pipeBinSize = 2)
fileList<-getFiles("~/Dropbox (Whiteley Lab)/BrownWhiteleyShare/2014_11_26RomanTIFFs/Experiment #2/wt abscess/wt abscess #2.1")  
NormRawPipeline(thresholdImage(fileList$c1,"red", 512),thresholdImage(fileList$c2,"green", 512),xysize=512, zsize=15,xydimSearch=13,zdimSearch=4,sampleSize=1000,xyRealDim=1.24,zRealDim=4, pipeBinSize = 2)
fileList<-getFiles("~/Dropbox (Whiteley Lab)/BrownWhiteleyShare/2014_11_26RomanTIFFs/Experiment #2/wt abscess/wt abscess #2.2")  
NormRawPipeline(thresholdImage(fileList$c1,"red", 512),thresholdImage(fileList$c2,"green", 512),xysize=512, zsize=10,xydimSearch=13,zdimSearch=4,sampleSize=1000,xyRealDim=1.24,zRealDim=4, pipeBinSize = 2)
fileList<-getFiles("~/Dropbox (Whiteley Lab)/BrownWhiteleyShare/2014_11_26RomanTIFFs/Experiment #2/wt abscess/wt abscess #2.3")  
NormRawPipeline(thresholdImage(fileList$c1,"red", 512),thresholdImage(fileList$c2,"green", 512),xysize=512, zsize=15,xydimSearch=13,zdimSearch=4,sampleSize=1000,xyRealDim=1.24,zRealDim=4, pipeBinSize = 2)
fileList<-getFiles("~/Dropbox (Whiteley Lab)/BrownWhiteleyShare/2014_11_26RomanTIFFs/Experiment #2/wt abscess/wt abscess #3.1")  
NormRawPipeline(thresholdImage(fileList$c1,"red", 512),thresholdImage(fileList$c2,"green", 512),xysize=512, zsize=17,xydimSearch=13,zdimSearch=4,sampleSize=1000,xyRealDim=1.24,zRealDim=4, pipeBinSize = 2)
fileList<-getFiles("~/Dropbox (Whiteley Lab)/BrownWhiteleyShare/2014_11_26RomanTIFFs/Experiment #2/wt abscess/wt abscess #3.2")  
NormRawPipeline(thresholdImage(fileList$c1,"red", 512),thresholdImage(fileList$c2,"green", 512),xysize=512, zsize=15,xydimSearch=13,zdimSearch=4,sampleSize=1000,xyRealDim=1.24,zRealDim=4, pipeBinSize = 2)